
The CrystGap share package provides functions for the computation 
with affine crystallographic groups, in particular space groups.  
It is loaded with the command
\beginexample 
     gap> RequirePackage( "cryst" ); 
\endexample

The present version 4.0 for {\GAP}~4 has been considerably reworked from
an earlier version for {\GAP}~3.4.4. Most of the porting to {\GAP}~4
has been done by Franz G{\accent127 a}hler. Besides `AffineCrystGroups'
acting from the right, also `AffineCrystGroups' acting from the left 
are now fully supported. Many algorithms have been added, extended, 
or improved in other ways.

Our warmest thanks go the Max Neunh{\accent127 o}ffer, whose extensive
testing of CrystGap in connection with XGAP uncovered several bugs and
led to many performance improvements.

CrystGap is implemented in the {\GAP}~4 language, and runs on any 
system supporting {\GAP}~4. However, certain commands may require 
that other share packages such as Carat or XGAP are installed.
In particular, the routines in Section 1.9 (normalizers) are likely
to require Carat, and the function WyckoffGraph requires XGAP. 
Both Carat and XGAP are available only under Unix.

CrystGap has been developed by
\beginitems
Bettina Eick &
Fachbereich 17,
Universit{\accent127 a}t Gesamthochschule Kassel,
D-34109 Kassel, Germany \hfill\break 
e-mail: `eick@mathematik.uni-kassel.de'

Franz G{\accent127 a}hler &
Institut f{\accent127 u}r Theoretische und Angewandte Physik,\hfil\break
Universit{\accent127 a}t Stuttgart,
D-70550 Stuttgart, Germany \hfill\break
e-mail: `gaehler@itap.physik.uni-stuttgart.de'

Werner Nickel &
Fachbereich Mathematik, AG2,
Technische Universit{\accent127 a}t Darmstadt, \hfill\break
Schlossgartenstra{\ss}e 7, D-64289 Darmstadt, Germany. \hfil\break
e-mail: `nickel@mathematik.tu-darmstadt.de'
\enditems

Please send bug reports, suggestions and other comments to any of these
e-mail addresses.

\vfill
Copyright {\copyright} 1999 
by Bettina Eick, Franz G\accent127ahler, and Werner Nickel.

\smallskip
CrystGap is subject to the {\GAP} copyright regulations as 
detailed in the copyright notice in the {\GAP} manual.






